---
title: "p8105_hw6_bh2852"
author: "Beicheng Huang"
date: "2023-12-03"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
library(modelr)
library(viridis)
library(mgcv)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


##Q1
Skip

##Q2

Weather data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

Set up Bootstrap samples

```{r}
boot_straps = 
  weather_df |>
  modelr::bootstrap(n = 5000) |>
  mutate(
    models = map(strap, \(df) lm(tmax ~ tmin + prcp, data = df)),
    results_1 = map(models, broom::tidy),
    results_2 = map(models, broom::glance)) |>
  select(-strap, -models)
```

###Estimating r2

```{r}
r2 = 
  boot_straps |>
  select(-results_1) |>
  unnest(results_2) |>
  select(.id, r.squared)
```

Plot the distribution of your estimates (r^2)

```{r}
r2 |> 
  ggplot(aes(x = r.squared)) + geom_density(fill = "orange")
```

Calculating 2.5% and 97.5% quantiles of r2, thus estimating 95%CI.

```{r}
lowerq_r2 <- quantile(r2$r.squared, 0.025)

upperq_r2 <- quantile(r2$r.squared, 0.975)

confidence_interval_r2 <- c(lowerq_r2, upperq_r2)

confidence_interval_r2
```
The estimated 2.5% quantile is 0.888 and 97.5% quantile is 0.941, thus the 95%CI is (0.888, 0.941)



###Estimating log(β^1∗β^2)

```{r}
logbeta = 
  boot_straps |>
  select(-results_2) |>
  unnest(results_1) |>
  select(.id, term, estimate) |>
  mutate(term = ifelse(term == "tmin", "b1", ifelse(term == "prcp", "b2", term))) |>
  pivot_wider(names_from = term, values_from = estimate) |>
  mutate(log_result = log(b1 * b2))
```

Plot the distribution of your estimates log(β^1∗β^2)

```{r}
logbeta |> 
  ggplot(aes(x = log_result)) + geom_density(fill = "violet")
```

According to the plot, it is a left-skewed distribution. 

Calculating 2.5% and 97.5% quantiles of log(β^1∗β^2), thus estimating 95%CI for log(β^1∗β^2)

```{r}
lowerq_log <- quantile(logbeta$log_result, 0.025, na.rm = TRUE)

upperq_log <- quantile(logbeta$log_result, 0.975, na.rm = TRUE)

confidence_interval_log <- c(lowerq_log, upperq_log)

confidence_interval_log
```
2.5% and 97.5% quantiles for log(β^1∗β^2) respectively are -9.069 and -4.593.Thus the 95% CI are (-9.069, -4.593).


##Q3

Load and clean the birthweight.csv datafile.

```{r}
birthweight_df = 
  read_csv("birthweight.csv") |>
  janitor::clean_names() |>
  drop_na() |>
  mutate(babysex = as.factor(babysex),
         frace = case_when(frace == 1 ~ "White",
                           frace == 2 ~ "Black",
                           frace == 3 ~ "Asian",
                           frace == 4 ~ "Puerto",
                           frace == 8 ~ "Other",
                           frace == 9 ~ "Unknown"),
         frace = as.factor(frace),
         malform = as.factor(malform),
         mrace = case_when(mrace == 1 ~ "White",
                           mrace == 2 ~ "Black",
                           mrace == 3 ~ "Asian",
                           mrace == 4 ~ "Puerto Rican",
                           mrace == 8 ~ "Other"),
         mrace = as.factor(mrace))
```
Hypothesis of linear regression model for birth weight.

```{r}
hypothesis = lm(bwt ~ babysex + bhead + blength + gaweeks + momage, data = birthweight_df)
```

Plotting the model residuals against fitted values.

```{r}
birthweight_df |>
  add_predictions(hypothesis) |>
  add_residuals(hypothesis) |>
  ggplot(aes(x = pred, y = resid)) + geom_point(alpha = 0.5)
```


Compare the model to two other models
```{r}
main_effect_model = lm(bwt ~ blength + gaweeks, data = birthweight_df)
three_way_interaction = lm(bwt ~ babysex + bhead + blength + babysex*bhead + babysex*blength + bhead*blength + babysex*bhead*blength, data = birthweight_df)
```

Modeling residual against fitted values for main effect model and three way interaction model.
```{r}
birthweight_df |>
  add_predictions(main_effect_model) |>
  add_residuals(main_effect_model) |>
  ggplot(aes(x = pred, y = resid)) + geom_point(alpha = 0.5)
```

```{r}
birthweight_df |>
  add_predictions(three_way_interaction) |>
  add_residuals(three_way_interaction) |>
  ggplot(aes(x = pred, y = resid)) + geom_point(alpha = 0.5)
```


Testing using cross-validation

Generate training and testing datasets
```{r}
cv_df = 
  crossv_mc(birthweight_df, 100) |>
 mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

Fit the model and obtain RMSEs using mutate and map&map2

```{r}
cv_df = 
  cv_df |> mutate(
    hypothesis  = map(train, \(df) lm(bwt ~ babysex + bhead + blength + gaweeks + momage, data = birthweight_df)),
    main_effect_model = map(train, \(df) lm(bwt ~ bhead + gaweeks, data = df)),
    three_way_interaction = map(train, \(df) lm(bwt ~ babysex + bhead + blength + babysex*bhead + babysex*blength + bhead*blength + babysex*bhead*blength, data = birthweight_df)))|> 
  mutate(
    rmse_hypo = map2_dbl(hypothesis, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_main = map2_dbl(main_effect_model, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_three = map2_dbl(three_way_interaction, test, \(mod, df) rmse(model = mod, data = df)))
```

Plot the prediction error for hypothesis, main effect, and three way interaction models.

```{r}
cv_df |> 
  select(starts_with("rmse")) |> 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") |> 
  mutate(model = fct_inorder(model)) |> 
  ggplot(aes(x = model, y = rmse)) + geom_violin(fill = "orange")
```

According to the graph, the hypothesis model which includes babysex + bhead + blength + gaweeks + momage as variables against birthweight seems to be the most appropriate model due to its lowest prediction error distribution. The three way interaction seems to be reasonable as well, while the main effect model has the largest prediction error distribution.
