---
title: "p8105_hw6_bh2852"
author: "Beicheng Huang"
date: "2023-12-03"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
library(modelr)
library(viridis)
library(mgcv)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


##Q1
Skip

##Q2

Weather data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

Set up Bootstrap samples

```{r}
boot_straps = 
  weather_df |>
  modelr::bootstrap(n = 5000) |>
  mutate(
    models = map(strap, \(df) lm(tmax ~ tmin + prcp, data = df)),
    results_1 = map(models, broom::tidy),
    results_2 = map(models, broom::glance)) |>
  select(-strap, -models)
```

###Estimating r2

```{r}
r2 = 
  boot_straps |>
  select(-results_1) |>
  unnest(results_2) |>
  select(.id, r.squared)
```

Plot the distribution of your estimates (r^2)

```{r}
r2 |> 
  ggplot(aes(x = r.squared)) + geom_density(fill = "orange")
```

Calculating 2.5% and 97.5% quantiles of r2, thus estimating 95%CI.

```{r}
lowerq_r2 <- quantile(r2$r.squared, 0.025)

upperq_r2 <- quantile(r2$r.squared, 0.975)

confidence_interval_r2 <- c(lowerq_r2, upperq_r2)

confidence_interval_r2
```
The estimated 2.5% quantile is 0.888 and 97.5% quantile is 0.941, thus the 95%CI is (0.888, 0.941)



###Estimating log(β^1∗β^2)

```{r}
logbeta = 
  boot_straps |>
  select(-results_2) |>
  unnest(results_1) |>
  select(.id, term, estimate) |>
  mutate(term = ifelse(term == "tmin", "b1", ifelse(term == "prcp", "b2", term))) |>
  pivot_wider(names_from = term, values_from = estimate) |>
  mutate(log_result = log(b1 * b2))
```

Plot the distribution of your estimates log(β^1∗β^2)

```{r}
logbeta |> 
  ggplot(aes(x = log_result)) + geom_density(fill = "violet")
```

According to the plot, it is a left-skewed distribution. 

Calculating 2.5% and 97.5% quantiles of log(β^1∗β^2), thus estimating 95%CI for log(β^1∗β^2)

```{r}
lowerq_log <- quantile(logbeta$log_result, 0.025, na.rm = TRUE)

upperq_log <- quantile(logbeta$log_result, 0.975, na.rm = TRUE)

confidence_interval_log <- c(lowerq_log, upperq_log)

confidence_interval_log
```
2.5% and 97.5% quantiles for log(β^1∗β^2) respectively are -9.069 and -4.593.Thus the 95% CI are (-9.069, -4.593).


##Q3

